Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-06-27 main_revision.tex
Updates from Overleaf

Other variables we tested in earlier versions of the analysis included rate constant controlling the growth and maintenance respiration rates, the fraction of ectomycorrhizal fungi, and parameters 'a' and 'b' of the flexible C:N ratio model. None of these had important impacts on the fertilization responses, and growth and respiration rates affected the model state in a linear and predictable fashion, thus they are omitted here but can be accessed via the available simulations.

>>>>

Other variables we tested in earlier versions of this analysis included rate constants controlling the growth and maintenance respiration rates, the fraction of ectomycorrhizal fungi, and parameters 'a' and 'b' of the flexible C:N ratio model. None of these had important impacts on the fertilization responses, and growth and respiration rates affected the model state in a linear and predictable fashion. They are omitted here for the sake of simplification, but data can be accessed via the available simulations.
